### 2022-09-12 draft.tex
Deploying to gh-pages from @ PoisotLab/manuscript-template@31363ca119e8c6a3d54b557e6f16021940d3167d 🚀
Deploying to gh-pages from @ PoisotLab/manuscript-template@895bf2fb607db28eae3d30e77d03a48206b7f6ce 🚀

%
\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
%
\,\textsuperscript{1,2,‡}\quad %
Peregrin\,Took%
%
\,\textsuperscript{3,4}\quad %
Merriadoc\,Brandybuck%
%
\,\textsuperscript{5,4,‡}

@@

\textsuperscript{‡}\,These authors contributed equally to the work\\

@@

        {\bfseries Purpose:}\,This template provides a series of scripts
to render a markdown document into an interactive website and a series
of PDFs.\\%
        {\bfseries Motivation:}\,It makes collaborating on text with
GitHub easier, and means that we never need to think about the
output.\\%
        {\bfseries Internals:}\,GitHub actions and a series of python
scritpts. The markdown is handled with \texttt{pandoc}.\\%

@@

\hypertarget{tbl:id}{}
\begin{longtable}[]{@{}rrrrl@{}}
\caption{\label{tbl:id}This is a table, and its identifier is
\texttt{id} -- we can refer to it using \texttt{\{@tbl:id\}}. Note that
even if the table legend is written below the table itself, it will
appear on top in the PDF document.}\tabularnewline
\toprule
Sepal.Length & Sepal.Width & Petal.Length & Petal.Width &
Species\tabularnewline
\midrule
\endfirsthead
\toprule
Sepal.Length & Sepal.Width & Petal.Length & Petal.Width &
Species\tabularnewline
\midrule
\endhead
5.1 & 3.5 & 1.4 & 0.2 & setosa\tabularnewline
5.0 & 3.6 & 1.4 & 0.2 & setosa\tabularnewline
5.4 & 3.9 & 1.7 & 0.4 & setosa\tabularnewline
\bottomrule
\end{longtable}

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-Camerano1880EquViv}{}%
Camerano, L. (1880). Dell'equilibrio dei viventi merce la reciproca
distruzione. \emph{Atti Della R. Accad. Delle Sci. Torino}, 15,
393--414.

\leavevmode\hypertarget{ref-Elton1927AniEco}{}%
Elton, C.S. (1927). \emph{Animal ecology}. University of Chicago Press.

>>>>

%
\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
%
\,\textsuperscript{,,}\quad %
Peregrin\,Took%
%
\,\textsuperscript{,}\quad %
Merriadoc\,Brandybuck%
%
\,\textsuperscript{,,}

@@

\textsuperscript{‡}\,Equal contributions\\

@@

@@

\hypertarget{tbl:id}{}
\begin{longtable}[]{@{}rrrrl@{}}
\caption{\label{tbl:id}This is a table, and its identifier is
\texttt{id} -- we can refer to it using \texttt{\{@tbl:id\}}. Note that
even if the table legend is written below the table itself, it will
appear on top in the PDF document.}\tabularnewline
\toprule()
Sepal.Length & Sepal.Width & Petal.Length & Petal.Width & Species \\
\midrule()
\endfirsthead
\toprule()
Sepal.Length & Sepal.Width & Petal.Length & Petal.Width & Species \\
\midrule()
\endhead
5.1 & 3.5 & 1.4 & 0.2 & setosa \\
5.0 & 3.6 & 1.4 & 0.2 & setosa \\
5.4 & 3.9 & 1.7 & 0.4 & setosa \\
\bottomrule()
\end{longtable}

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-Camerano1880EquViv}{}}%
Camerano, L. (1880). Dell'equilibrio dei viventi merce la reciproca
distruzione. \emph{Atti Della R. Accad. Delle Sci. Torino}, 15,
393--414.

\leavevmode\vadjust pre{\hypertarget{ref-Elton1927AniEco}{}}%
Elton, C.S. (1927). \emph{Animal ecology}. University of Chicago Press.
